opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-12-04 chapters/04_our_dataset.tex
Added overview table with checkmarks idea

\begin{table}[!htb]
\centering
\caption{opXRD database entries}
\label{tab:merged}
\begin{tabular}{@{}clccccl@{}}
\toprule
Institution & No. Patterns & Spg & Lattice & Unit Cell & Comp. & Research Project \\ 
\midrule
CNRS        & \qquad 895          & $\times$   & $\times$   & $\times$   & $\times$   & Extracted from the COD                 \\ 
HKUST(GZ)   & \qquad 21           & $\times$   & $\times$   & $\times$   & $\times$   & Phase identification reference database \\ 
USC         & \qquad 338          & $\times$   & $\times$   &            & $\times$   & Study of CuNi and CuAl alloys          \\ 
EMPA        & \qquad 790          & $\times$   &            &            & $\times$   & Tin halide perovskites, Zn-V-N library \\ 
INT         & \qquad 19780        &            &            &            &            & Compilation of various projects        \\ 
IKFT        & \qquad 64           &            &            &            &            & Commercial catalysts, bulk materials   \\ 
LBNL        & \qquad n/a          &            &            &            &            & Time series recordings of Perovskites  \\ 
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[!htb]
\centering
\caption{opXRD database entries}
\label{tab:merged}
\begin{tabular}{@{}clcccccl@{}}
\toprule
Institution & No. Patterns & Comp. & Spg & Lattice & Unit Cell & Research Project \\ 
\midrule
CNRS        & \qquad 895          & \cmark   & \cmark   & \cmark   & \cmark   & Extracted from the COD                 \\ 
HKUST(GZ)   & \qquad 21           & \cmark   & \cmark   & \cmark   & \cmark   & Phase identification reference database \\ 
USC         & \qquad 338          & \cmark   & \cmark   & \cmark   & \xmark   & Study of CuNi and CuAl alloys          \\ 
EMPA        & \qquad 790          & \cmark   & \cmark   & \xmark   & \xmark   & Tin halide perovskites, Zn-V-N library \\ 
INT         & \qquad 19780        & \xmark   & \xmark   & \xmark   & \xmark   & Compilation of various projects        \\ 
IKFT        & \qquad 64           & \xmark   & \xmark   & \xmark   & \xmark   & Commercial catalysts, bulk materials   \\ 
LBNL        & \qquad n/a          & \xmark   & \xmark   & \xmark   & \xmark   & Time series recordings of Perovskites  \\ 
\bottomrule
\end{tabular}
\end{table}
